\documentclass[12pt,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[scale=0.75]{geometry}

\firstname{Jeremy}
\familyname{Lacomis}

% \title{Resume}
\address{Street Redacted}{Charlottesville, VA 22903}
\phone{(555) 123 4567}
\email{lacomis@virginia.edu}


\begin{document}
\makecvtitle

\section{Education}
\cventry{2015--Present}{Computer Science}{University of
  Virginia}{Charlottesville, VA}{}{
  \begin{itemize}
  \item Research Assistant.
  \item Completed a graduate-level programming languages seminar requiring
    reading and presenting several journal and conference publications per
    week.
  \end{itemize}}
\cventry{2012--2015}{A.S. Computer Science}{Piedmont Virginia Community
  College}{Charlottesville, Virginia}{\textit{Summa Cum Laude}}{
  \begin{itemize}
  \item 4.0 GPA
  \end{itemize}}
\cventry{2005--2006}{Electrical Engineering}{Rochester Institute of
  Technology}{Rochester, NY}{}{
  \begin{itemize}
  \item Robotics Club
  \end{itemize}}

\section{Experience}
\cventry{2016}{Research Assistant}{University of Virginia}{Charlottesville,
  VA}{}{Gained experience with the entire research process including developing
  new research ideas and hypotheses, experimental design, data analysis and
  interpretation, and writing scientific papers.\\
  Detailed achievements:
  \begin{itemize}
    \item Developed an automated technique for finding power optimizations in
      software using search-based software engineering.
    \item Designed algorithmic modifications that allow the technique to
      scale to datacenter-scale applications.
    \item Designed and constructed cost-effective low-noise hardware for rapidly
      sampling power usage in servers.
    \item Paper submitted to Transactions on Software Engineering.
  \end{itemize}}
\cventry{2011--2015}{Manager}{Brixx Wood-Fired Pizza}{Charlottesville, VA}{}{}
\cventry{2006--2009}{Field Service Engineer}{Expert Imaging}{Charlottesville,
  VA}{}{Maintained and repaired medical scanners including CT, MRI, X-Ray, and
  ultrasound.
  \begin{itemize}
  \item Managed parts sales, acquisition, and inventory.
  \item Specialized experience with Siemens MRI scanners and MRI subsystems
    including superconducting magnets, radio frequency signal generation and
    amplification, cryogenics, computer systems, and HVAC.
  \item Experienced with client interaction including communicating
    domain-specific technical concepts to non-experts through conversation and
    written service reports.
  \end{itemize}}

\section{Languages}
\cvitem{Experienced}{bash, C++, OCaml, Python}
\cvitem{Proficient}{C, Java}
\cvitem{Familiar}{Haskell, HTML, Javascript, Lisp, Objective-C, Scheme, Ruby,
  x86 Assembly}

\section{Skills}
\cvlistitem{Experience with emacs, Eclipse, git, make, gdb, \LaTeX}
\end{document}
